\documentclass[10pt,a4paper]{article}

\usepackage[margin=3cm]{geometry}
\usepackage{amsmath,amsthm}
\allowdisplaybreaks
\usepackage[bitstream-charter]{mathdesign}
\usepackage[T1]{fontenc}
\usepackage[pdftex,bookmarksopen,
            pdftitle={Errata to Tikhonov and Landweber convergence rates},
            pdfauthor={},
            colorlinks,linkcolor=black,urlcolor=black,citecolor=black]{hyperref}

\newcommand{\IR}{\mathbb{R}}
\newcommand{\IN}{\mathbb{N}}
\newcommand{\IT}{\mathbb{T}}
\newcommand{\IX}{\mathbb{X}}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
\newcommand{\norm}[2]{     \| #1       \|_{ #2 }}
\newcommand{\Norm}[2]{\left\| #1 \right\|_{ #2 }}
\newcommand{\normiii}[2]{\vert\kern-0.25ex\vert\kern-0.25ex\vert #1 \vert\kern-0.25ex \vert\kern-0.25ex\vert_{ #2 }}
\newcommand{\Normiii}[2]{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert_{ #2 }}
\newcommand{\scalar}[2]{     \langle #1       \rangle_{ #2 }}
\newcommand{\Scalar}[2]{\left\langle #1 \right\rangle_{ #2 }}

\newtheorem{remark}{Remark}

\begin{document}

\title{Errata to\\
\emph{Tikhonov and Landweber convergence rates:\\ characterization by interpolation spaces}}
\author{}
\date{\today}
\maketitle

\begin{abstract}
This note records errata for the paper \emph{Tikhonov and Landweber convergence rates: characterization by interpolation spaces}.  Equation, section, lemma, and proposition numbers refer to the arXiv version \url{https://arxiv.org/abs/1503.05742v4}.  The errata list below states the corrections succinctly, and the subsequent notes give detailed justifications for selected items.
\end{abstract}

\section*{Errata list}

\begin{enumerate}

\item[\textup{(E1)}]
In equation (6), the displayed value
\[
    \alpha
    =
    t^{1/k}
    \left(\frac{1-\theta}{\theta}\right)^{1-1/(2k)}
\]
is meaningful only for $0<\theta<1$.  The endpoint cases $\theta=0,1$ should be treated separately, or obtained by a limiting argument.

\item[\textup{(E2)}]
In Section 2.3, the sentence claiming that the distance function $d$ has compact support if and only if $x\in X_1$ is not valid for an arbitrary continuous embedding $X_1\subset X$.  It should be deleted, or stated under an additional closedness assumption on the embedded balls of $X_1$ in $X$.

\item[\textup{(E3)}]
The identity (9)--(10) is false as stated.  The quantity
\[
    E
    :=
    \sup_{r>0}
    \inf_{\norm{x_1}{1}\le r}
    \norm{x-x_1}{0}^{1-\theta}
    \norm{x_1}{1}^{\theta}
\]
does not equal $N_\theta^{-1}\norm{x}{\theta:1}$ in general.  The valid identity is
\[
    N_\theta^{-1}\norm{x}{\theta:1}
    =
    D,
    \qquad
    D:=\sup_{r>0}d(r)^{1-\theta}r^\theta .
\]
Consequently, the proof of (9), in particular step c), should be replaced.

\item[\textup{(E4)}]
In Lemma 2.1, the quantifier in inequality (13) should read
\[
    \forall\,\gamma>\nu
\]
instead of $\forall\,\gamma>0$.

\item[\textup{(E5)}]
In the proof of Proposition 2.2, inequality (26a), after the substitution $s:=t^{1/\gamma}$ the term
\[
    s^2\int_{[s,\infty)}\lambda^{-2\gamma}\,d\mu_x(\lambda)
\]
should be
\[
    s^{2\gamma}\int_{[s,\infty)}\lambda^{-2\gamma}\,d\mu_x(\lambda).
\]
Equivalently, one may keep the term as $t^2\int_{[s,\infty)}\lambda^{-2\gamma}\,d\mu_x(\lambda)$ until substituting $s=t^{1/\gamma}$.

\item[\textup{(E6)}]
In the proof of Proposition 2.2, inequality (26b), the displayed choice
\[
    t=s^\gamma\sqrt{\frac{\gamma-\nu}{\nu}}
\]
is meaningful only for $0<\nu<\gamma$.  The endpoint case $\nu=0$ should be handled separately.

\item[\textup{(E7)}]
Definitions and statements involving the quotient $\nu/\gamma$ require $\gamma>0$.  In particular, the definition of $X_{\nu:\gamma}$ and Proposition 2.4 should be read with this restriction whenever $\nu/\gamma$ appears.

\item[\textup{(E8)}]
The lower-bound part of the proof of Proposition 2.4 should not invoke the false $E$-identity in (9)--(10).  It should use only the corrected distance-function identity
\[
    N_\nu^{-1}\norm{x}{\nu:1}
    =
    \sup_{r>0}d(r)^{1-\nu}r^\nu,
\]
or be replaced by a direct Hilbert-space duality argument.

\item[\textup{(E9)}]
Equations (55)--(56) contain an incorrect minimization problem and an inconsistent parameter scaling.  To keep (55) with the factor $\alpha^{-\nu}$, equation (56) should read
\[
    x_{\alpha:\gamma}
    :=
    \argmin_{x\in X}
    \left\{
        \norm{(T^*T)^{\gamma/2}(x^\dag-x)}{}^2
        +
        \alpha^\gamma\norm{x-x_0}{}^2
    \right\}.
\]
Equivalently, if a parameter $\beta$ is placed in front of $\norm{x-x_0}{}^2$, then the middle term in (55) should be
\[
    \sup_{\beta>0}
    \beta^{-\nu/\gamma}
    \norm{x^\dag-x_{\beta:\gamma}}{} .
\]

\item[\textup{(E10)}]
In the proof of Proposition 3.2, the appeal to equation (6) does not literally cover the endpoint cases $\nu=0$ and $\nu=k$.  The proposition is correct, but these two cases should be justified separately.

\item[\textup{(E11)}]
The residual representation (64) is missing the factor $\sigma$.  It should read
\[
    y^\dag-Tx_k
    =
    (I-\sigma TT^*)^k(y^\dag-Tx_0),
    \qquad
    y^\delta-Tx_k^\delta
    =
    (I-\sigma TT^*)^k(y^\delta-Tx_0).
\]

\item[\textup{(E12)}]
For general step size $\sigma$, the noisy Landweber splitting (65) should contain a factor $\sqrt{\sigma}$.  Namely,
\[
    \norm{x^\dag-x_k^\delta}{}
    \le
    \norm{x^\dag-x_k}{}
    +
    \delta\sqrt{\sigma k}.
\]
The printed estimate is valid after the normalization $\sigma=1$, or under an additional harmless adjustment of constants when $\sigma$ is fixed.

\item[\textup{(E13)}]
In equation (67), the factor $(1+k/\nu)^\nu$ requires $\nu>0$.  Thus the surrounding statement should not allow $\nu=0$ without a separate convention.

\item[\textup{(E14)}]
In the proof of Proposition 3.4, equation (74) is preceded by the claim that $\varepsilon_k$ maximizes
\[
    \lambda^{2(r+\nu)}(1-\sigma\lambda)^{2k}
\]
over $\lambda\ge0$.  The correct maximization domain is the spectral interval
\[
    0\le\lambda\le1/\sigma .
\]

\item[\textup{(E15)}]
In the paragraph following equation (87), the sufficient condition for the discrepancy principle has the inequality reversed.  To ensure
\[
    \norm{y^\dag-Tx_k}{}\le\delta(\tau-1),
\]
one needs
\[
    c_2\varepsilon_k^{\nu+1/2}
    \normiii{x^\dag-x_0}{\nu}
    \le
    \delta(\tau-1),
\]
not the reverse inequality.

\item[\textup{(E16)}]
The asymptotic estimate displayed in equation (84) after Proposition 3.4 is written in the normalization $\sigma=1$.  For general $\sigma$, the factor
\[
    \varepsilon_k^{r+\nu}
    =
    \sigma^{-(r+\nu)}
    \left(\frac{r+\nu}{k+r+\nu}\right)^{r+\nu}
\]
contributes the corresponding power of $\sigma$.

\end{enumerate}


\input{erratum_E1_Ncomm_endpoint}

\input{erratum_E2_distance_compact_support}

\input{erratum_E3_distance_identity}

\input{erratum_E4_lemma_mu_gamma_range}

\input{erratum_E5_prop22_cutoff_power}

\input{erratum_E6_prop22_endpoint_nu0}

\input{erratum_E7_gamma_positive}

\input{erratum_E8_prop24_lower_bound}

\input{erratum_E9_tikr_gamma_parameter}

\input{erratum_E10_tikk_endpoints}

\input{erratum_E11_landweber_residual_sigma}

\input{erratum_E12_landweber_noise_splitting_sigma}

\input{erratum_E13_landweber_qok_nu0}

\input{erratum_E14_landweber_argmax_domain}

\input{erratum_E15_discrepancy_inequality}

\input{erratum_E16_landweber_sigma_asymptotic}

\end{document}
